Index measures for oak decline severity using phenotypic descriptors

### 2019-12-15 manuscript/manuscript.Rmd
added disscussion point

- reasons for selecting machine learing approach
- use of unsupervised over supervised analysis
- Semi-supervised can be used if unsupervised model is unable to pull out decline severity scale
- For given context, descriptors not contributing to the indexes could be removed
- Concession of model interpretability to predictive capability by using a machine learning approach
- seen as black box but LIME and response surfaces enable interpretation and therefore trust

>>>>

- reasons for selecting machine learing approach
- use of unsupervised over supervised analysis
- Semi-supervised can be used if unsupervised model is unable to pull out decline severity scale
- For given context, descriptors not contributing to the indexes could be removed
- Concession of model interpretability to predictive capability by using a machine learning approach
- seen as black box but LIME and response surfaces enable interpretation and therefore trust
- LIME can be applied to out of place cases
